Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-30 doc/PRF2022/PRF_main.tex
updated figures

\begin{figure}[h!]
\begin{center}
  \includegraphics[height=0.27\textheight]{Nb198a_inset.pdf}
  \includegraphics[height=0.27\textheight]{Nb198b_eta_inset.pdf}\\
  \hspace{1.55cm}
  \includegraphics[height=0.27\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.27\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles self-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
    All figure insets are configurations using $N_b=60$ sharing with the same color map.}
\end{caption}
\end{figure}

@@

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
\includegraphics[width=0.49\textwidth]{relax_E.pdf}
\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. The near-equilibrium configurations depend on the initial configuration and the results show that 
    the striated configurations have largest value of order parameter for both $N_b=60$ and $N_b=198$ cases.
  }
\end{figure}

@@

%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in shear flow}
%\end{figure}
%\begin{figure}
%\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
%\end{figure}
\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=600$). The streamlines are plotted in the background. }
\end{figure}

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=500$, respecitively. The streamlines are plotted in the background.}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
  \hspace{-1cm}
  \includegraphics[height=0.27\textheight]{Nb198a_inset.pdf}
  \hspace{-0.85cm}
  \includegraphics[height=0.27\textheight]{Nb198b_eta_inset.pdf}\\
  \includegraphics[height=0.27\textheight]{Nb198c_eta_inset.pdf}
  \includegraphics[height=0.27\textheight]{Nb198d_eta_inset.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows $N_b = 198$ particles confined to a square with random 
  positions and orientation.
  Depending on the boundary condition \eqref{eq:bc-type},
  the particles self-assemble into distinct configurations.
  Panel (b) is for $b=1$ and the boundary condition mimicks that
  of an amphiphilic particle. 
  Panel (c) is for $b=2$ which gives rise to a multilamellar configuration. 
  In panel (d), the case $b = 0$ is for a water structure with
  positive/negative charge. 
  The false color maps use blue for $u < 0$, green for $u = 0$, and yellow then red for $u > 0$.
    All figure insets are configurations using $N_b=60$ sharing with the same color map.}
\end{caption}
\end{figure}

@@

\begin{figure}
  \begin{center}
%  \includegraphics[width=0.49\textwidth]{Relax_Energy_inset.pdf}
%\includegraphics[width=0.49\textwidth]{relax_E.pdf}
%\includegraphics[width=0.49\textwidth]{relax_LOP.pdf} 
\includegraphics[width=1.0\textwidth]{relax_E_LOP.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
  A:  The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles. B: The local order parameter $\tilde{S}_2$ for all 6 relaxation runs. The near-equilibrium configurations depend on the initial configuration and the results show that 
    the striated configurations have largest value of order parameter for both $N_b=60$ and $N_b=198$ cases.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
      \includegraphics[width=0.22\textwidth]{VS_0.pdf}
      \includegraphics[width=0.22\textwidth]{VS_1.pdf}
   \includegraphics[width=0.22\textwidth]{VS_2.pdf}
   \includegraphics[width=0.22\textwidth]{VS_3.pdf}\\
         \includegraphics[width=0.22\textwidth]{BS_0.pdf}
      \includegraphics[width=0.22\textwidth]{BS_1.pdf}
   \includegraphics[width=0.22\textwidth]{BS_2.pdf}
   \includegraphics[width=0.22\textwidth]{BS_3.pdf}
%   Panels (e)-(f) same but for non-vesicle initial configuration
  \end{center}
  \caption{
    \label{fig:BC1_shear_flow}
    The figure shows a vesicle in shear flow (panel (a) shows the pre-relaxed initial configuration; panels (b)-(d): $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=160$) 
    and the multiple component bilayers in shear flow (The insets of Fig~\ref{fig:relax}b is used for panels (e); panels (f)-(h): $\dot \gamma = \{0.05, 0.075, 0.1\}$ at $t=500$). The streamlines are plotted in the background. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}\\
      \includegraphics[width=0.3\textwidth]{BS_E.pdf}
   \includegraphics[width=0.3\textwidth]{BS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{BS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Comparisons between vesicle (top row) and bilayer (bottom row) configurations: Energy $E(t)$, local order parameter $\tilde{S}_2(t)$, and the mean square displacement $MSD(t)$. Shear rates are $\dot\gamma=\{0.05, 0.0655, 0.75\}$. The shear rate $\dot\gamma = 0.0655$ are picked from ~\cite{Fu2022_JFM} where it is known to be the critical shear rate for ruptures and the trend is clearly distinguished from all three measures. For the bilayer configurations, as shown in Fig~\ref{fig:relax}, multiple bialyer structures are placed in shear flows. The supplementary movies show that a slower shear flow results menbrane fusions and $\tilde{S}_2(t)$ increases in the long run.
     }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.22\textwidth]{MS_0.pdf}
  \includegraphics[width=0.22\textwidth]{MS_1.pdf}
  \includegraphics[width=0.22\textwidth]{MS_2.pdf} 
    \includegraphics[width=0.22\textwidth]{MS_3.pdf} 
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC2_shear_flow} Multi-lamellar stracture in shear flows. The insets of Fig~\ref{fig:relax}c is used for panels (a). Panels (b)-(d) are snapshots when shear rates are $\dot\gamma=\{0.05, 0.1, 0.15\}$ at $t=600$, respecitively. The streamlines are plotted in the background.}
\end{figure}

@@
